---
title: "Skill Test 3"
output: html_document
date: "2024-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.Load and clean FacultySalaries_1995.csv file and Re-create the graph below…
```{r FacultySalary, echo=TRUE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(modelr)
library(easystats)
library(broom)
library(fitdistrplus)
library(janitor)

dat <- read.csv("../Exam_3/Exam_3/FacultySalaries_1995.csv")
View(dat)

str(dat)
head(dat)

dat1 <- dat %>%
  pivot_longer(cols = starts_with("Avg"), 
               names_to = c("Rank", "Metric"), 
               names_pattern = "Avg(.*)(Prof.*)", 
               values_to = "Value") %>% 
  filter(Rank %in% c("Full", "Assoc", "Assist")) %>%
  filter(Tier != "VIIB")  

view(dat1)

unique(dat1$Rank)

gragh1 <- ggplot(dat1, aes(x = Rank, y = Value, fill = Rank)) +
  geom_boxplot(size = 1) +
  facet_wrap(~Tier,) +  
  scale_fill_manual(values = c("lightpink2", "seagreen3", "cadetblue")) + 
  labs(x = "Rank",
       y = "Salary",
       fill = "Rank") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
```

2.Build an ANOVA model and display the summary output in your report.

```{r ANOVAmodel, echo=TRUE}
dat1$State <- as.factor(dat1$State)
dat1$Tier <- as.factor(dat1$Tier)
dat1$Rank <- as.factor(dat1$Rank)

mod <- aov(Value ~ State + Tier + Rank, data = dat1)
summary(mod)
report(mod)
```

3. The rest of the test uses another data set. The “Juniper_Oils.csv” data. Get it loaded and take a look. Then tidy it! (show the code used for tidying in your report)
```{r}
data <- read.csv("../Exam_3/Exam_3/Juniper_Oils.csv")
View(data)
str(data)
colnames(data)

chem <- c(
  "alpha.pinene", "para.cymene", "alpha.terpineol", "cedr.9.ene", "alpha.cedrene",
  "beta.cedrene", "cis.thujopsene", "alpha.himachalene", "beta.chamigrene", "cuparene",
  "compound.1", "alpha.chamigrene", "widdrol", "cedrol", "beta.acorenol",
  "alpha.acorenol", "gamma.eudesmol", "beta.eudesmol", "alpha.eudesmol",
  "cedr.8.en.13.ol", "cedr.8.en.15.ol", "compound.2", "thujopsenal"
)

data1 <- data %>%
  pivot_longer(
    cols = all_of(chem),
    names_to = "ChemicalID",
    values_to = "Concentration"
  )

view(data1)
```


4. Make me a graph of the following:
```{r}
gragh2 <- ggplot(data1, aes(x = YearsSinceBurn, y = Concentration)) +
  geom_smooth(se = TRUE, color = "blue", alpha = 0.5) +  
  facet_wrap(~ ChemicalID, scales = "free_y") + 
  labs(x = "Years Since Burn",
       y = "Concentration") +
  theme_minimal() 
```

5. Use a generalized linear model to find which chemicals show concentrations that are significantly (significant, as in P < 0.05) affected by “Years Since Burn”.
```{r}
data2 <- data1 %>%
  group_by(ChemicalID) %>% 
  do({
    glm_model <- glm(Concentration ~ YearsSinceBurn, data = ., family = gaussian()) 
    broom::tidy(glm_model) %>% filter(term == "YearsSinceBurn") 
  }) %>%
  ungroup() %>%
  filter(p.value < 0.05) %>% 
  dplyr::select(ChemicalID, term, estimate, std.error, statistic, p.value)
view(data2)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
