---
title: "Skill Test 3"
output: html_document
date: "2024-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.Load and clean FacultySalaries_1995.csv file and Re-create the graph below…

```{r FacultySalary, echo=TRUE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(modelr)
library(easystats)
library(broom)
library(fitdistrplus)

dat <- read.csv("../Exam_3/Exam_3/FacultySalaries_1995.csv")
View(dat)

str(dat)
head(dat)

dat1 <- dat %>%
  pivot_longer(cols = starts_with("Avg"), 
               names_to = c("Rank", "Metric"), 
               names_pattern = "Avg(.*)(Prof.*)", 
               values_to = "Value") %>% 
  filter(Rank %in% c("Full", "Assoc", "Assist")) %>%
  filter(Tier != "VIIB")  

view(dat1)

unique(dat1$Rank)

ggplot(dat1, aes(x = Rank, y = Value, fill = Rank)) +
  geom_boxplot(size = 1) +
  facet_wrap(~Tier,) +  
  scale_fill_manual(values = c("lightpink2", "seagreen3", "cadetblue")) + 
  labs(x = "Rank",
       y = "Salary",
       fill = "Rank") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

```

2.Build an ANOVA model and display the summary output in your report.

```{r ANOVAmodel, echo=TRUE}
dat1$State <- as.factor(dat1$State)
dat1$Tier <- as.factor(dat1$Tier)
dat1$Rank <- as.factor(dat1$Rank)

mod <- aov(Value ~ State + Tier + Rank, data = dat1)
summary(mod)
report(mod)

```

3. The rest of the test uses another data set. The “Juniper_Oils.csv” data. Get it loaded and take a look. Then tidy it! (show the code used for tidying in your report)

4. Make me a graph of the following:

5. Use a generalized linear model to find which chemicals show concentrations that are significantly (significant, as in P < 0.05) affected by “Years Since Burn”.



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
